The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-14 methods/ms.tex
Pointing plot - gauss

\newcommand{\ammonia}{\mbox{{\rm NH}$_3$}}
\newcommand{\form}{H$_2$CO}
\newcommand{\td}{\mbox{$T_D$}}
\newcommand{\jj}[2]{\mbox{$J = #1\rightarrow#2$}}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{{\tt jaguirre@sas.upenn.edu}}
\newcommand{\lsim}{{_{<}\atop^{\sim}}}
\newcommand{\gsim}{{_{>}\atop^{\sim}}}
\newcommand{\etal}{{et al.\/}}
\newcommand{\ie}{{\em ie.\/}}
\newcommand{\cmq}{cm{$^{-3}$}}
\newcommand{\per}{$^{\rm{-1}}$}
\newcommand{\tc}{{$\theta^1$~Orionis~C}}
%\newcommand{\msol}{M{$_{\odot}$}}
\def\msol{\ifmmode {\>M_\odot}\else {$M_\odot$}\fi}
\newcommand{\lsol}{L{$_{\odot}$}}
\newcommand{\kms}{km~s{$^{-1}$}}
\newcommand{\hii}{H~{\sc ii}}
\newcommand{\Hii}{H~{\sc ii}}
\newcommand{\Ha}{\mbox{H$\alpha$}}
\newcommand{\sii}{S~{\sc ii}}
\newcommand{\Feii}{Fe~{\sc ii}}
\newcommand{\oi}{O~{\sc i}}
\newcommand{\nii}{N~{\sc ii}}
\newcommand{\oiii}{O~{\sc iii}}
\newcommand{\mgii}{Mg~{\sc ii}}
\newcommand{\tco}{{$^{13}$CO}}
\newcommand{\CO}{{$^{12}$CO}}
\newcommand{\Tco}{{$^{12}$CO}}
\newcommand{\co}{C{$^{18}$O}}
\newcommand{\Lsol}{L$_{\odot}$}
\newcommand{\Msol}{M$_{\odot}$}
%\newcommand{\C18o}{C$^{18}$O($1\rightarrow 0$)}
\newcommand{\Check}{{\bf ???}}
\newcommand{\mum}{\ensuremath{\mu \mathrm{m}}}
\newcommand{\flux}{flux density}
\newcommand{\solar}{\ensuremath{\odot}}
\newcommand{\long}{\ensuremath{\ell}}

@@

\begin{figure}
  \hspace{-1in}
  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
  1.5$\deg. The large scale 'peanut' shape including DR21 is suggestive of a
  large wind-blown bubble, although.... [someone else must have commented on
  this in the past?].  See section \ref{sec:motte} for a comparison with the
  \citet{motte2007} IRAM study of this region. }
\end{figure}
%  \vspace{-4in}

@@

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution.]
{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{paper_gaussian_0707}}

>>>>

\newcommand{\ammonia}{\mbox{{\rm NH}$_3$}}
\newcommand{\form}{H$_2$CO}
\newcommand{\td}{\mbox{$T_D$}}
\newcommand{\jj}[2]{\mbox{$J = #1\rightarrow#2$}}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{{\tt jaguirre@sas.upenn.edu}}
\newcommand{\lsim}{{_{<}\atop^{\sim}}}
\newcommand{\gsim}{{_{>}\atop^{\sim}}}
\newcommand{\etal}{{et al.\/}}
\newcommand{\ie}{{\em ie.\/}}
\newcommand{\cmq}{cm{$^{-3}$}}
\newcommand{\per}{$^{\rm{-1}}$}
\newcommand{\tc}{{$\theta^1$~Orionis~C}}
%\newcommand{\msol}{M{$_{\odot}$}}
\def\msol{\ifmmode {\>M_\odot}\else {$M_\odot$}\fi}
\newcommand{\lsol}{L{$_{\odot}$}}
\newcommand{\kms}{km~s{$^{-1}$}}
\newcommand{\hii}{H~{\sc ii}}
\newcommand{\Hii}{H~{\sc ii}}
\newcommand{\Ha}{\mbox{H$\alpha$}}
\newcommand{\sii}{S~{\sc ii}}
\newcommand{\Feii}{Fe~{\sc ii}}
\newcommand{\oi}{O~{\sc i}}
\newcommand{\nii}{N~{\sc ii}}
\newcommand{\oiii}{O~{\sc iii}}
\newcommand{\mgii}{Mg~{\sc ii}}
\newcommand{\tco}{{$^{13}$CO}}
\newcommand{\CO}{{$^{12}$CO}}
\newcommand{\Tco}{{$^{12}$CO}}
\newcommand{\co}{C{$^{18}$O}}
\newcommand{\Lsol}{L$_{\odot}$}
\newcommand{\Msol}{M$_{\odot}$}
%\newcommand{\C18o}{C$^{18}$O($1\rightarrow 0$)}
\newcommand{\Check}{{\bf ???}}
\newcommand{\mum}{\ensuremath{\mu \mathrm{m}}}
\newcommand{\flux}{flux density}
\newcommand{\solar}{\ensuremath{\odot}}
\newcommand{\lon}{\ensuremath{\ell}}

@@

\begin{figure}
  \hspace{-1in}
  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
  1.5\deg$. The large scale 'peanut' shape including DR21 is suggestive of a
  large wind-blown bubble, although.... [someone else must have commented on
  this in the past?].  See section \ref{sec:motte} for a comparison with the
  \citet{motte07} IRAM study of this region. }
\end{figure}
%  \vspace{-4in}

@@

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution.]
{\label{fig:PointingModel-b}\includegraphics[scale=1.0]{paper_gaussian_0707}}
